---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Coviddata

<!-- badges: start -->
<!-- badges: end -->

Coviddata contains a Shiny app which provides the information about the Covid-19.Download the package to use the shiny app can explore the data through the table,map and a plot.

Download this package and know more about the details.

## Installation

You can install the released version of Coviddata from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Coviddata")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-KarinaZou")
```
## Example

This is a basic example show you how to launch the app::

```{r example}
#library(Coviddata)
#Coviddata::launch_app()
```



You can also embed plots, for example:

```{r pressure, echo = FALSE}

```


